### 2020-06-04 writeup/experiments.tex
sec 3
quick pass

\begin{table}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf IncTrain} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{xx\%} \\
		{\bf LSTM} & \textbf{36\%} & xx\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
	\vspace{-0.2in}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
	\vspace{-0.2in}
\end{minipage}
\end{table}

@@

{\bf Datasets and models.} We describe the datasets and models we use in the experiments.

{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.

{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

@@

For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.

\textbf{Training procedures and baselines.} We use round-robin training schedule for the MTL model.
We compare our incremental training scheduler of Algorithm \ref{alg_inc_train} to the round-robin training scheduler.
We focus on the prediction accuracy of a particular target task.

@@

\textbf{Improving multi-task training efficiency.}
We compare Algorithm \ref{alg_inc_train} to performing multi-task learning for predicting a particular target dataset.
Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

\textbf{Improving transfer learning training efficiency.}
We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.

\textbf{MTL improves data efficiency ratio.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ ({\cor or $36\%$?}) of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task similarity}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
	(c) As source/target data ratio increases, the performance gain from the covariance alignment procedure \cite{WZR20} over MTL increases for LSTM and MLP.}
	\label{fig_ablation}
	\vspace{-0.15in}
\end{figure}

@@

\textbf{Explaining .} In Figure \ref{fig_ablation}, we validate the three components of our theory on the sentiment analysis dataset.
The experimental procedure is left to Appendix \ref{app_it}.

\textbf{Understanding MTL results via STL results.}
We show that STL results can be used to help understand MTL results.
We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
The results show that STL performances are indicative of MTL performances.

>>>>

\begin{table}[!b]
\begin{minipage}[t]{.40\textwidth}
	\vspace{-0.1in}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		Sentiment\\ analysis\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf IncTrain} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{xx\%} \\
		{\bf LSTM} & \textbf{36\%} & xx\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\vspace{-0.1in}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\end{table}

@@

We consider a text classification task and an image classification task as follows.

{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer with GloVe embeddings
followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

@@

%\textbf{The training procedure and baseline.}
For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
The baseline training schedule for MTL is the round-robin training schedule.
%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
We measure the test accuracy of predicting a target task.

@@

Our first result is to show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
Our insight is that since adding more samples from the source task does not always improve performance, we can improve efficiency by adding the source samples \textit{incrementally} during training.
Over six randomly selected task pairs from the sentiment analysis dataset, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.

We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ ({\cor or $36\%$?}) of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task similarity}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer (red curve).
	(c) As source/target sample ratio increases, the performance gain of aligning task covariances \cite{WZR20} compared to MTL increases for LSTM and MLP.}
	\label{fig_ablation}
	\vspace{-0.15in}
\end{figure}

@@

A common challenge in the study of multi-task learning is that the results can be hard to understand.
It is difficult to predict when MTL performs well without running extensive trials.
Our insight here is that we can use STL results to help understand MTL results.
We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
The results show that STL results are indicative of MTL results.

Finally, we validate our theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
In Figure \ref{fig_ablation}, we show that MTL performance is affected by
(a) decreased task similarity;
(b) increased source/target sample ratio;
(c) covariate shift under increased source sample size.
For the last result, specifically we show that the alignment procedure proposed in \cite{WZR20} becomes more helpful when the sample ratio is large.
The experimental procedure is left to Appendix \ref{app_it}.

### 2020-06-04 writeup/intro.tex
intro
quick pass

\vspace{-0.2in}
\begin{abstract}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task model distance}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
	We formally quantify each component in the setting of high-dimensional linear regression,
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of the multi-task estimator determines the effect of transfer..
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) increased task model distance;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	We validate the above results on text classification tasks.
	Inspired by our theory, we show that single-task performance can help understand multi-task performance, and propose an incremental training scheduler for improving the efficiency of multi-task training.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

>>>>

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.1in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
	We formally quantify each component in the setting of high-dimensional linear regression,
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of the multi-task estimator determines the effect of transfer..
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) decreased task similarity;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	We validate the above results on text classification tasks.
	Inspired by our theory, we show that single-task performance can help understand multi-task performance, and propose an incremental training scheduler for improving the efficiency of multi-task training.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

### 2020-06-04 writeup/related.tex
quick pass

\textbf{Multi-task learning theory.}
Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their results do not apply to explain the phenomena of negative transfer.

% Adding a regularization over $B$, e.g. .
\textbf{Multi-task learning methodology.}
Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,R17}.
We believe that the technical tools we have developed can also be applied to many other multi-task learning models.

\textbf{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}. For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}. It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}. On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}. To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.

>>>>

\textit{Multi-task learning theory.}
Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
Our work is closely related to Wu et al. \cite{WZR20}.
While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their results do not apply to explain the phenomena of negative transfer.

% Adding a regularization over $B$, e.g. .
\textit{Multi-task learning methodology.}
Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,R17}.
We believe that the technical tools we have developed can also be applied to many other multi-task learning models.

\textit{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}. For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}. It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}. On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}. To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.

### 2020-06-04 writeup/transfer.tex
quick pass

%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
We show theoretical implications for understanding the performance of multi-task learning.
(a) \textit{Task model distance}: we explain the phenomenon of negative transfer precisely as task models become different.
(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
Finally, we extend our result from two tasks to many tasks with the same features.
%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%We show how negative transfer occurs by varying task similarity or sample size.
%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.

@@

\subsection{Task Model Distance}\label{sec_similarity}

@@

Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
We can see that our result is able to predict positive or negative transfer  accuractly that matches the empirical curve.
There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
%Figure \ref{fig_model_shift} shows the result.
%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
%The proof of Proposition \ref{prop_dist_transition} involves two parts.
%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.

>>>>

%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
We show theoretical implications for understanding the performance of multi-task learning.
(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
Finally, we extend our result from two tasks to many tasks with the same features.
%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%We show how negative transfer occurs by varying task similarity or sample size.
%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.

@@

\subsection{Task Similarity}\label{sec_similarity}

@@

Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
We can see that our result is able to predict positive or negative transfer  accuractly that matches the empirical curve.
There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
%Figure \ref{fig_model_shift} shows the result.
%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
%The proof of Proposition \ref{prop_dist_transition} involves two parts.
%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
